### 2021-10-14 NSF2021/Description/specificaim1.tex
starting nsf 2021

\section{Proposed Research}
\label{sec:proposed-work}
%The proposed research develops fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
%%
We have demonstrated that our hydrophobic attraction with repulsion
potential (HAP) approach efficiently simulates self-assembly of
amphiphilic particles into two-dimensional micelles, bilayer membranes,
and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
phenomenon in external shear flows \cite{FuQuRyYo20}.
While the results show great promise in the field of collective body
hydrodynamics, several outstanding issues need to be addressed. These
include a thorough analysis of elastic properties of our coarse-grained
bilayers and efficiently simulating three-dimensional collective
hydrodynamics of amphiphilic particles.
We must also incorporate electric charge and account
for how external fields control particle self-assembly. 
%mathematically
%characterize the variational behavior of HARP under appropriate
%homogenized limits.

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
%\end{center}
%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
%\label{fig:distortions}
%\end{figure}
The goal of Specific Aim 1 is to characterize the material properties of
many-body, self-assembled amphiphiles.  For amphiphiles assembled into
bilayers, these properties are described by membrane continuum
mechanics.  Our goal is to map the parameters of the particle-based
model onto the elastic moduli from continuum theory.  Results from this
goal will facilitate simulators to use the hydrophobic attraction force
calculations to model bilayers with specific composition. These
calculations have provably less computational complexity than those of
molecular dynamics simulations and possess the molecular granularity
lacking from continuum models.

Hamm and Kozlov (HK) pioneered the modern theory of membrane continuum
mechanics~\cite{Hamm2000}, and their theory is widely used to describe
biological phenomena, including fission \cite{FrEsAkSh15, Maetal15,
PhysRevE.79.031926}, fusion \cite{ChKo08,
KoKo2002,Kuzmin7235,Aeffner2012}, poration~\cite{Gaetal20}, phase
boundaries, and interaction with inclusions~\cite{SeLeMaEg17,Saetal20,
Pietal20}. These phenomena require resolution of the internal structure
of the membrane.  Recently, there has been a revival of interest in the
HK theory as the quadratic assumption for the elasticity energy density
has caused researchers to question the applicability of the theory for
large curvatures~\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.46\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

%\begin{wrapfigure}[13]{l}{0.5\textwidth}
%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
%diaphragm expansion (ii) and pore formation (iii). 
%(B) Saddle-splay energy for each change in \emph{monolayer} topology
%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
%\label{fig:barriers}
%\end{wrapfigure}

\sloppy
The HK framework assumes a three-dimensional lipid monolayer where the internal structure
consists of straight fibers that represent elongated hydrocarbon chains.
The elastic energy density ${\cal W}$ is quadratic in the Green-Lagrange strain
tensor for this striated, internal structure.
%
%
%
%These fibers
%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
%Accordingly, the deformation takes the form 
%\begin{equation}
%  \label{LMdeformation}
%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
%\end{equation}
%where $(X_1,X_2,X_3)$ are points in a reference volume.
%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
%
%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
%The chains stretch and compress to satisfy incompressibility.
%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
%lead to an elastic surface energy over the dividing surface $\Sigma$. 
%
This energy density decomposes into four, fundamental, and independent
deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
the unit surface normal;
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, 
%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
%Also, the surface divergence 
%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
%respectively (Figure \ref{fig:distortions}A--C).
the deformations come with elastic coefficients: the bending modulus
$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
$\KTH$.
%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
%
The parameter $k_0$ is the spontaneous curvature and determines the
preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
%As an illustration, the
%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
%%as a result of  %having a relatively long acyl chain. 
%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
%because the addition of a positive splay 
%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
%The subtraction of $k_0^2$ makes the energy distortion free
%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.

Although the HK elastic theory assumes small deformations, 
Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
Under spatial scales much larger than the membrane thickness, membrane
energy is well-characterized by the Canham-Helfrich energy used
throughout the fluid-structure literature \cite{QiangDu09,
Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014,
qua-vee-you2019}. The Canham-Helfrich energy is actually a special case
of \eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the
$\pm$ depending on orientation) and collapsing both monolayers onto the
membrane midplane.
%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
%are equal to zero.

%\begin{figure}
%\begin{center}
%\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
%\end{center}\vspace{-1.em}
%\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
%The quartic fit comes from continuum theory. 
%(B) A circular vesicle at equilibrium. (C) The area modulus derives
%from convexity in energy as a function of radius. 
%\label{fig:bend}}
%\end{figure}

% Proposers should address what they want to do,
% why they want to do it,
% how they plan to do it,
% how they will know if they succeed,
% and what benefits could accrue if the project is successful.
%\begin{center}
%Preliminary results
%\end{center}

%\begin{wrapfigure}[13]{l}{0.5\textwidth}
%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
%diaphragm expansion (ii) and pore formation (iii). 
%(B) Saddle-splay energy for each change in \emph{monolayer} topology
%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
%\label{fig:barriers}
%\end{wrapfigure}

%\begin{center}
%Anticipated model simulations
%\end{center}
\newpage
\subsubsection{Simulations of the HAP model to estimate elastic moduli
and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
\begin{wrapfigure}[11]{r}{0.43\textwidth}
%\vspace{-0.4cm}
\centerline{\includegraphics[width=0.42\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
%\vspace{-0.5cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
We propose to {\bf (i)} determine the value of effective elastic moduli
$\KB$, $\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the
model parameters $\rho,$ $\gamma$, and the particle shape map onto
elastic moduli. An accurate and robust way to measure material
properties is to track the evolution of the bilayer as it relaxes from
an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}.
Figure~\ref{fig:flattening} shows an example where the initial
configuration of a bilayer patch containing the splay deformation
without any other components (saddle splay, twist and tilt). As the bent
membrane flattens, both the self-interaction energy $\Phi$ and the
elastic energy ${\cal W}$ decrease, and because the saddle splay, twist,
and tilt stay zero, the slope gives the bending modulus in this case.

%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
%We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
%$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
%%
%%Motivated by our preliminary results \cite{Fu2018_SIAM}
%%we use realistic values for particle diameter $2$ nm \cite{Boal},
%%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
%%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
%%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
%%particle diameter and the hydrophobic boundary condition \eqref{SL}
%%are additional parameters defining the coarse-grained representation. 
%
%An accurate and robust way to measure material properties is to track the evolution of the bilayer.

Here we start with a particle-based bilayer in a specific
non-equilibrium shape that involves only one of the components of the
displacement in Figure~\ref{fig:deformations}, and then evolve the
particle system according to the time integration for \eqref{eq:stokes}.
Because elastic properties are independent of dissipation, we can forgo
solving for fluid velocity and set the translational velocity and
angular velocity directly proportional to the force and torque,
respectively. 
%bilayer by steepest gradient descent 
%with respect to the HARP functional:
%\begin{equation}
%\label{SGD}   
%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
%\end{equation}
%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
%The procedure involves solving \eqref{SL} based off of the current particle configuration.
%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
%through \eqref{SGD}.
%

@@

%In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
%When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
%and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.

%
%Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
%The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
%the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
%energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
%Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
%These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
%as required by fussion and fission. 
%
%Bending is the energetically most consequential deformations. To measure a bending modulus,  
%we deform the midplane of a planar bilayer into the shape of a circular arc.
%This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
%The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
%In the case of a rectangular bialyer, the corresponding elastic energy 
%$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
%Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
%used to values for infer $\KB$.

%
We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
for other elastic moduli such as the effective twist modulus $\KT$.
Molecular dynamics investigations find a twist modulus about 1
\kBT~\cite{LeVeWa14}, and here, the specific non-equilibrium shape consists of
a single layer of amphiphilic particles on a hydrophobic substrate as
illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
requires nonzero tilt because the surface gradient of the lipid
director equals the second fundamental form
%, and is therefore symmetric,
whenever tilt is zero locally. The twist deformation is a fully
three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.

%for a wide range of particle parameters and physical parameters in HARP to 
%
%We will also determine the effective saddle splay modulus $\KG$. 
The gradient descent technique is ineffective for measuring the saddle splay modulus $\KG$ because
the saddle splay energy is largely invariant under shape changes.
To evaluate $\KG$, we will combine the present particle simulations with the string method 
from PI RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
In the simplified Canham-Helfrich formulation, saddle splay energy is an exact indicator of topological transitions, 
thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
As a result, saddle splay can be quantified from the transition energies
of a least energy path of pore formation  (Figure 6).
%(Figure \ref{fig:saddle_splay}).   
%Using the string method, we will evaluate the transition energies between the intact pancake shape,
%and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
%to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations. 
%
%%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
%%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
%%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
%%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
%%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
%%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively. 
%
%The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
%As discussed earlier, recent disagreement in elastic moduli between continuum model and MD simulations originates from such assumption. 
%The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
%\subsubsection{HK elastic energy form}

%\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to
whether HK energy is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. 
A value $\KT = 0$, however, makes~\eqref{ansatz3} a noncoercive functional.
%and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
term that was neglected from the HK analysis~\cite{Hamm2000}.
Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
identified an inconsistency in the argument used
by~\cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200} that gives rise to a larger energy barrier for
monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
\begin{wrapfigure}[11]{l}{0.32\textwidth}
\centerline{\includegraphics[width=0.31\textwidth]{Figures/SaddleSplayDiagram.pdf}}
%  \vspace{-8pt}
\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
  saddle splay modulus.}
\end{wrapfigure}
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

% The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
% liquid crystal theory. However, the ``bend'' distortion from nematics  
% is not present in monolayers since the directors have no dependence in the normal direction.
% There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.

@@

%The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
%Also, the boundary layers of the solutions to the screen Laplace equation
%converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
%These phenomena are analogous to the sharp interface limit in the phase-field functional,
%and motivate developing the mathematical connections between the HAP energy and
%the energy functionals used in the gradient theory of phase transitions.
%formulation~\cite{Modica87, MODICA1987487, LuMo89}.
%PI RR has worked on phase field approximations of membrane bending
%energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
%equation~\cite{1531-3492_2006_2_357, Lee2018}.
%The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
%One set of questions is to establish the HAP convergence rate as a
%function of particle geometry~\cite{LuMo89}, which can be used as a
%benchmark for numerical validation.
%Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
%particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
%The phase field functional approximates the perimeter of sublevel sets
%of a so-called phase field indicator function. The approximation becomes
%sharp in the zero interfacial thickness limit and minimizers of the
%phase field functional converge (after normalization) to the
%characteristic function of a set solving a perimeter minimization
%problem
%
%

%In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
%As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
%We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
%\begin{equation}
%\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
%\end{equation}
%$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
%\cite{https://doi.org/10.1038/s41467-019-09787-6}
%
%
%% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
%% whether \eqref{ansatz3} contains a complete list of consistent deformations.
%%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
%%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
%%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
%%  \textbf{(ii)}
%%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
%%  Later, \cite{C9SM02079A} 
%%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
%%  from a transversal tilt invariance assumption.
%%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
%%  \textbf{(iii)}
%%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
%%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
%%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
%%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
%%suggesting a somewhat smaller magnitude for $\KG$.
%
% 
%%The form of the elastic energy density \eqref{ansatz3} is the same as

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
%%
We have demonstrated that our hydrophobic attraction with repulsion
potential (HAP) approach efficiently simulates self-assembly of
amphiphilic particles into two-dimensional micelles, bilayer membranes,
and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
phenomenon in external shear flows \cite{FuQuRyYo20}.
While the results show great promise in the field of collective body
hydrodynamics, several outstanding issues need to be addressed. These
include a thorough analysis of elastic properties of our coarse-grained
bilayers and efficiently simulating three-dimensional collective
hydrodynamics of amphiphilic particles.
We must also incorporate electric charge and account
for how external fields control particle self-assembly.

@@

The goal of Specific Aim 1 is to investigate generalizations of the
screened Laplace equation for different soft matter systems.

\begin{comment}
The goal of Specific Aim 1 is to characterize the material properties of
many-body, self-assembled amphiphiles.  For amphiphiles assembled into
bilayers, these properties are described by membrane continuum
mechanics.  Our goal is to map the parameters of the particle-based
model onto the elastic moduli from continuum theory.  Results from this
goal will facilitate simulators to use the hydrophobic attraction force
calculations to model bilayers with specific composition. These
calculations have provably less computational complexity than those of
molecular dynamics simulations and possess the molecular granularity
lacking from continuum models.

Hamm and Kozlov (HK) pioneered the modern theory of membrane continuum
mechanics~\cite{Hamm2000}, and their theory is widely used to describe
biological phenomena, including fission \cite{FrEsAkSh15, Maetal15,
PhysRevE.79.031926}, fusion \cite{ChKo08,
KoKo2002,Kuzmin7235,Aeffner2012}, poration~\cite{Gaetal20}, phase
boundaries, and interaction with inclusions~\cite{SeLeMaEg17,Saetal20,
Pietal20}. These phenomena require resolution of the internal structure
of the membrane.  Recently, there has been a revival of interest in the
HK theory as the quadratic assumption for the elasticity energy density
has caused researchers to question the applicability of the theory for
large curvatures~\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.46\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory.

\sloppy
The HK framework assumes a three-dimensional lipid monolayer where the
internal structure consists of straight fibers that represent elongated
hydrocarbon chains.  The elastic energy density ${\cal W}$ is quadratic
in the Green-Lagrange strain tensor for this striated, internal
structure. This energy density decomposes into four, fundamental, and
independent deformations (Figure~\ref{fig:deformations}): splay ($\Div
{\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf
n}$), and tilt ${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where
${\bf N}$ is the unit surface normal;
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, the deformations come with elastic coefficients: the bending
modulus $\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt
modulus $\KTH$. The parameter $k_0$ is the spontaneous curvature and
determines the preferred lipid splay~\cite{RoLi15,Kozlov2007}.

Although the HK elastic theory assumes small deformations, Galimzyanov
{\em et al.}~\cite{C9SM02079A} have shown that energies derived from
molecular dynamics and those derived from \eqref{ansatz3} are in
agreement, even when curvatures are large.  Under spatial scales much
larger than the membrane thickness, membrane energy is
well-characterized by the Canham-Helfrich energy used throughout the
fluid-structure literature \cite{QiangDu09, Lowengrub07,KimLai2010_JCP,
Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014, qua-vee-you2019}. The
Canham-Helfrich energy is actually a special case of \eqref{ansatz3}
obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
orientation) and collapsing both monolayers onto the membrane midplane.

\subsubsection{Simulations of the HAP model to estimate elastic moduli
and energy}
\begin{wrapfigure}[11]{r}{0.43\textwidth}
  \centerline{\includegraphics[width=0.42\textwidth]{Figures/Flattening.pdf}}
  \caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
We propose to {\bf (i)} determine the value of effective elastic moduli
$\KB$, $\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the
model parameters $\rho,$ $\gamma$, and the particle shape map onto
elastic moduli. An accurate and robust way to measure material
properties is to track the evolution of the bilayer as it relaxes from
an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}.
Figure~\ref{fig:flattening} shows an example where the initial
configuration of a bilayer patch containing the splay deformation
without any other components (saddle splay, twist and tilt). As the bent
membrane flattens, both the self-interaction energy $\Phi$ and the
elastic energy ${\cal W}$ decrease, and because the saddle splay, twist,
and tilt stay zero, the slope gives the bending modulus in this case.

Here we start with a particle-based bilayer in a specific
non-equilibrium shape that involves only one of the components of the
displacement in Figure~\ref{fig:deformations}, and then evolve the
particle system according to the time integration for \eqref{eq:stokes}.
Because elastic properties are independent of dissipation, we can forgo
solving for fluid velocity and set the translational velocity and
angular velocity directly proportional to the force and torque,
respectively.

@@

We propose to conduct calculations similar to the example of
Figure~\ref{fig:flattening} for other elastic moduli such as the
effective twist modulus $\KT$.  Molecular dynamics investigations find a
twist modulus about 1 \kBT~\cite{LeVeWa14}, and here, the specific
non-equilibrium shape consists of a single layer of amphiphilic
particles on a hydrophobic substrate as illustrated by
Figure~\ref{fig:deformations}D. Having a nonzero twist requires nonzero
tilt because the surface gradient of the lipid director equals the
second fundamental form whenever tilt is zero locally. The twist
deformation is a fully three-dimensional deformation.
\S\ref{subsec:specific_aim_3} addresses outstanding implementation
issues like three-dimensional boundary integral equation solvers.

The gradient descent technique is ineffective for measuring the saddle
splay modulus $\KG$ because the saddle splay energy is largely invariant
under shape changes.  To evaluate $\KG$, we will combine the present
particle simulations with the string method from PI RR's work on
membrane fusion \cite{RyKlYaCo16}. The string method is a numerical
scheme that finds least energy pathways separating energy basins
\cite{doi:10.1063/1.2720838}.  In the simplified Canham-Helfrich
formulation, saddle splay energy is an exact indicator of topological
transitions, thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
More generally, PI RR has shown that saddle splay acts as a topological
indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.  As a
result, saddle splay can be quantified from the transition energies of a
least energy path of pore formation (Figure~\ref{fig:saddle_splay}).

The field of membrane continuum mechanics still lacks consensus as to
whether HK energy is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral
fluidity in membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. A value $\KT = 0$, however, makes~\eqref{ansatz3}
a noncoercive functional. \textbf{(ii)} Recently,~\cite{TerziDeserno17}
derived a tilt curvature term that was neglected from the HK
analysis~\cite{Hamm2000}.  Later,~\cite{C9SM02079A}
and~\cite{PhysRevE.102.042406} independently identified an inconsistency
in the argument used by~\cite{TerziDeserno17} arising from a transversal
tilt invariance assumption.  In~\cite{RyKlYaCo16}, PI RR and
collaborators showed that the tilt vector leads to unphysical cusps
depending on how one accounts for membrane thickness.  \textbf{(iii)}
Theoretical analysis of lipid phase transitions predict a negative
saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200} that gives rise to a larger energy barrier for monolayer
fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
\begin{wrapfigure}[11]{l}{0.32\textwidth}
  \centerline{\includegraphics[width=0.31\textwidth]{Figures/SaddleSplayDiagram.pdf}}
  \caption{\label{fig:saddle_splay} \footnotesize Example of determining
  the saddle splay modulus.}
\end{wrapfigure}

@@

\end{comment}
